Invasive lionfish present region-wide variation of allometric growth in the Western Atlantic

### 2018-06-01 docs/Manuscript.tex
Updated manuscript, ready for (last?) round of revision with Sean

\author[1]{Juan Carlos Villaseñor-Derbez\(^1\), Sean Fitzgerald}
\affil[1]{Bren School of Environmental Sciences and Management, University of
California Santa Barbara, Santa Barbara, California, USA}
\corrauthor[1]{Juan Carlos Villaseñor-Derbez}{jvillasenor@bren.ucsb.edu}

% \keywords{A, B, C}

\begin{abstract}
Lionfish (\emph{Pterois volitans/miles}) are an invasive species in the
Western Atlantic and the Caribbean. Improving management of invasive
lionfish populations requires accurate estimates of total biomass, which
in turn depend on accurate definition of the length-weight relationship.
Here, we reviewed published length-weight relationships of lionfish
taken from throughout their invasive range and found that lionfish of
equal lengths have lower body mass in the Caribbean than in the Atlantic
or Gulf of Mexico. Additionally, we report a new pair of length-weight
parameters (\(a = 3.2056 \times 10^{-6}; b = 3.235\)) for organisms
sampled in the central Mexican Caribbean region. The substantial spatial
variation in length-weight parameters highlights the importance of using
site-specific information when estimating lionfish biomass using length
observations. These findings can have major implications for management
in terms of predicting effects on local ecosystems, evaluating the
effectiveness of removal programs, or estimating biomass available for
harvest.
\end{abstract}

@@

Lionfish (\emph{Pterois volitans/miles} complex) are an invasive species
in the western Atlantic and the Caribbean, likely introduced through
liberation of aquarium-kept organisms \citep{betancurr_2011}. They are
the first invasive marine vertebrates established along the North
Atlantic Caribbean coasts
\citep{schofield_2009,schofield_2010,sabidoitza_2016} and their presence
has been labeled as a major marine invasion because they threaten local
biodiversity, spread rapidly, and are difficult to manage
\citep{hixon_2016}. Invasive lionfish are primarily studied in coral
reef ecosystems, where their impacts are far-reaching. For example,
field experiments by \citet{albins_2008} showed that lionfish
establishment led to reduced recruitment of native fishes by nearly 80\%
over a five week period in Florida, and increased lionfish biomass
coincided with a 65\% reduction in the biomass of native prey fishes
along Bahamian coral reefs in just two years \citep{green_2012}.
Lionfish have also established invasive populations in other habitats
such as estuaries, mangroves , hard-bottomed areas , and mesophotic
reefs
\citep{jud_2011,barbour_2010,muoz_2011,andradibrown_2017,claydon_2012}.

A substantial amount of research describes lionfish feeding ecology from
North Carolina to Costa Rica
\citep{muoz_2011,morris_2009,cote_2013,dahl_2014,valdezmoreno_2012,villaseorderbez_2014,hackerott_2017,sandel_2015}.
A meta-analysis by \citet{peake_2018} showed that invasive lionfish prey
on at least 167 different species across the tropical and temperate
North Atlantic. Their feeding behavior and high consumption rates can
reduce recruitment and population sizes of native reef-fish species, and
can further endanger reef fish
\citep{albins_2008, green_2012,rocha_2015}. (However, see
\citet{hackerott_2017} for a case where there was no evidence that
lionfish affected the density, richness, or community composition of
prey fishes). Major efforts have been made to understand the possible
impacts of the invasion by tracking the spread of established lionfish
populations through time \citep{schofield_2009,schofield_2010} and by
predicting invasion ranges under future climates \citep{grieve_2016}.
Trophic impacts of lionfish can be minimized if local lionfish biomass
is controled by by culling \citep{ariasgonzalez_2011}. However, the
feasability of controling local populations remains a topic of debate
\citep{cote_2014}.

@@

The feasibility of establishing fisheries through lionfish removal
programs has been extensively evaluated through field observations and
empirical modeling
\citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,chin_2016,usseglio_2017}.
One contributing factor to the success of many removal programs is the
sedentary nature of adult lionfish \citep{jud_2012}. Culling programs
are effective in reducing adult populations largely because lionfish
exhibit high levels of site fidelity and rarely leave their home range
in most cases \citep{Fishelson_1997,cote_2014,kochzius_2005} -- But see
\citet{andradibrown_2017} for cases when deep-water populations maintain
shallow-water populations. Fish with this sedentary behavior are likely
to exhibit high levels of spatial variation in important life history
characterstics such as growth or natural mortality rate
\citep{hutchinson_2008,wilson_2012}. The importance of considering
spatial heterogeneity is well-documented in terms of assessing and
managing sedentary species \citep{gunderson_2008,guan_2013}, and such
variation should be accounted for when evaluating the feasibility of
establishing lionfish fisheries as well.

Empirical modeling efforts examining the feasibility of establishing
fisheries for lionfish involve modeling changes in biomass in response
to changes in mortality (\emph{i.e.} culling). A common way to model
this is via length-structured population models, where fish lengths are
converted to weight in order to calculate total biomass
\citep{cote_2014,barbour_2011,andradibrown_2017}. The length-weight
relationship is therefore an essential component of these models, but
this relationship can vary across regions as a response to biotic
(e.g.~local food availability) and abiotic (e.g.~water temperature)
conditions \citep{johnson_2016}. Literature suggests that site-specific
parameters are necessary in order to accurately estimate biomass when
length-weight relationships are spatially variable , and this
variability becomes increasingly important when estimating the potential
effectiveness of (and resources needed for) lionfish culling programs or
when identifying total biomass available for harvest by fishers
\citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}. In
addition to environmentally-driven spatial variation, genetic analysis
of invasive lionfish suggest biological differences due to the existence
of two genetically distinct subpopulations between the northwest
Atlantic and the Caribbean \citep{betancurr_2011}. To date, no studies
have examined region-wide differences in length-weight parameters
despite the large number of studies reporting this relationship for
lionfish.

@@

We reviewed 12 published studies and obtained 17 length-weight
relationships for the North Atlantic (n = 1), Gulf of Mexico (n = 7,),
and Caribbean (n = 10, Table \ref{tab:all_params}, Fig
\ref{fig:all_allo}). We collected information on sampling methods, sex
differentiation, location, and depth ranges from each study when
available, and assumed both genders were included in a study if gender
was unspecified. Two studies reported parameters for genders combined an
separated \citep{aguilarperera_2016,fogg_2013}, while the rest presented
pooled results. Reviewed studies presented information for organisms
obtained at depths between 0.5 and 57 m. Three studies explicitly stated
that their organisms were sampled with pole spears
\citep{aguilarperera_2016,chin_2016,dahl_2014,sabidoitz_2016}, and five
studies mentioned that some of their organisms were obtained with pole
spears (or other type of harpoon) but also hand-held nets or fish traps
\citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,sabidoitz_2016,toledohernndez_2014},
and two studies did not specify how organisms were sampled
\citep{deleon_2013,darling_2011}. \citet{fogg_2013} use spine-less
weight in the length-weight relationship estimation, and thus their
parameters likely underestimate whole wieght. Since no spine-less to
whole weight conversions were available, these parameters were taken as
reported.

@@

Combining the length-weight parameters extracted from the literature and
the additional pair calculated here, we obtain a total of 18 pairs. We
use the central Mexican Caribbean as a case study of how the use of
\emph{ex situ} parameters influences the accuracy of weight estimates
for lionfish. We estimated TW from the TL observations we collected in
the central Mexican Caribbean (n = 109) using each of the 18 parameter
pairs and divided predicted weights by known observed weights to obtain
a simple measure of over- or underestimation. Difference in mean weight
ratios across the different parameter pairs were tested with a one-way
analysis of variance (ANOVA). All analyses were performed in R version
3.5.0 \citep{rcore_2018} . Raw data and code used in this work are
available at dryad.org.

@@

Inserting TL observations for the central Mexican Caribbean into
\ref{eq:log-alo} Eq. 2 and converting to \ref{eq:log-alo-trans} resulted
in the coefficient values \(b = 3.2347391\) and \(c = -5.4940866\)
(\(R^2 = 0.977\), F(df = 1; 107) = 6928.67, \(p < 0.001\)). The
length-weight coefficients estimated in this study were within the range
identified by studies in other regions (Table \ref{tab:all_params}). The
significant difference between this allometric factor (\(b\)) and the
isometric growth factor \(b = 3\) (\(t(107) = 6.04; p<0.001\)) indicated
that lionfish present allometric growth, which is consistent with other
studies. Figure \ref{fig:l-w-carib} shows the relationship between TL
and TW for this region, and more information on model fit is presented
in Table S2.

Parameters from models fit to males or females exclusively tend to have
a higher steepness (\emph{i.e.} higher allometric parameter), with mean
\(\pm\) standard deviation values of \(b = 3.27 \pm 0.06\) and
\(b = 3.31 \pm 0.23\) for males and females respectively, compared to
parameters from models for pooled genders with a mean \(\pm\) standard
deviation value of \(b = 3.14 \pm 0.20\). In the case of the ponderal
index (\(a\)) and its \(log_{10}\) transformation (\(c\)), values were
higher for parameters for pooled genders. Figure \ref{fig:all_allo}
shows the length-weight relationships with parameters from all studies.

There were significant differences in our predicted weights for the
central Mexican Caribbean when using the different pairs of parameters
(\(F(df = 15; 1728) = 38.26; p < 0.001\)). The lowest weight estimates
resulted from using the allometric parameters from Banco Chinchorro in
the Caribbean \citet{sabidoitz_2016}, and the highest weight estimates
came from the Northern Atlantic\citet{barbour_2011}. The calculated
ratio of predicted-to-observed weight ranged from 0.80 \(\pm\) 0.19 to
1.76 \(\pm\) 0.50 (mean \(\pm\) SD). Predicted-to-observed weight ratios
are presented in Figure \ref{fig:bio_ratio}. Spine-less weight
parameters from \citet{fogg_2013} still produced predicted-to-observed
weight rations \textgreater{} 1.

@@

\caption{\label{tab:unnamed-chunk-5}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study. All parameters have been adjusted to convert from millimeters to grams. n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter for Eq. 1 (presented in $\times 10^{-5}$), c = y-intercept for Eq. 3, b = exponent or slope for Eq. 1 or Eq. 3, respectively. The $R^2$ column indicates reported model fit.}
\centering
\begin{tabular}[t]{llllrrll}
\toprule
Region & Sex & n & a & b & c & \$R\textasciicircum{}2\$ & Reference\\
\midrule
Caribbean & B & 458 & 3.6 & 2.81 & -4.44 & - & Sandel et al., 2015\\
Caribbean & B & 419 & 2.8 & 2.85 & -4.56 & 0.8715 & Chin et al., 2016\\
Caribbean & B & 1450 & 2.3 & 2.89 & -4.64 & 0.96 & de Leon et al., 2013\\
Caribbean & B & 1887 & 0.3 & 3.24 & -5.52 & 0.97 & Edwards et al., 2014\\
Caribbean & B & - & 0.25 & 3.29 & -5.60 & - & Darling et al., 2011\\
\addlinespace
Caribbean & B & 2143 & 0.52 & 3.18 & -5.28 & 0.9907 & Sabido-Itza et al., 2016\\
Caribbean & B & 227 & 0.8 & 3.11 & -5.10 & 0.958 & Toledo-Hernández et al., 2014\\
Caribbean & B & 449 & 0.23 & 3.25 & -5.64 & 0.97 & Sabido-Itza et al., 2016b\\
Caribbean & B & 368 & 0.32 & 3.19 & -5.50 & 0.98 & Sabido-Itza et al., 2016b\\
Caribbean & B & 109 & 0.32 & 3.23 & -5.49 & 0.9766 & This study\\
\addlinespace
GoM & B & 934 & 0.21 & 3.34 & -5.68 & 0.98 & Dahl \& Patterson, 2014\\
GoM & B & 472 & 0.29 & 3.30 & -5.54 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & F & 67 & 0.12 & 3.47 & -5.93 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & M & 59 & 0.42 & 3.23 & -5.38 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & B & 582 & 0.14 & 3.43 & -5.86 & 0.99 & Fogg et al., 2013\\
\addlinespace
GoM & M & 119 & 0.27 & 3.31 & -5.57 & 0.97 & Fogg et al., 2013\\
GoM & F & 115 & 0.68 & 3.14 & -5.17 & 0.94 & Fogg et al., 2013\\
NorthAtlantic & B & 774 & 2.9 & 2.89 & -4.54 & - & Barbour et al.,2011\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
\caption{\label{fig:all_allo}Length-weight relationships (n = 18) for 12
studies and this study. Colors indicate studies from which the
parameters were extracted. Solid lines indicate that the fit was
performed for males and females pooled together. Dotted lines indicate
that the regression was performed on females, and dashed lines indicate
it was performed for males. The dashed black line represents the
relationship estimated in this study.}
\end{figure}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
\caption{\label{fig:bio_ratio}Violin plot of predicted to observed
weight ratios for 18 pairs of allometric parameters. Red and blue
circles indicate median and mean values, respectively. Like letters
indicate values that do not differ significantly (Tukey's HSD; p
\textless{} 0.05).}
\end{figure}

@@

We detected substantial differences in weight-at-length between
organisms from the Caribbean and Gulf of Mexico / North-Western
Atlantic. Weight estimates using parameters from the Gulf of Mexico and
North-Western Atlantic were higher on average than those from the
Caribbean. The average predicted-to-observed weight ratios from these
three regions were insert 1.24 \(\pm\) 0.309, 1.76 \(\pm\) 0.496, and
Caribbean 1.17 \(\pm\) 0.398, respectively. These length-weight
differences mirror similar findings of regional variability in
age-at-length relationships of lionfish across both their invaded and
native regions \citep{pusack_2016}. These differences may be driven by
genetic variation or by organisms being exposed to distinct
environmental conditions. For example, \citet{betancurr_2011} used
mitochondrial DNA to demonstrate the existence of two distinct
population groups, identified as the ``Caribbean group'' and ``Northern
Group'', and \citet{fogg_2015} alternatively suggested that
age-at-length differences may be driven by climate. Differences in
weight-at-length could also reflect differences in energy input
(\emph{i.e.} in some regions, lionfish eat more) or differential usage
of this energy (\emph{e.g.} regional differences in predator abundances
lead to different usage of energy), or a combination of both. Future
research is needed to determine which processes are at work here.

Differences in length-weight relationships have traditionally been
highlighted as potential pitfalls to fishery management. For example,
\citet{wilson_2012} show that small-scale variations in length-at-age
and fishing mortality in other Scorpaeniformes (\emph{Sebastes
rastrelliger}) translate to differential landings, effort, and catch per
unit effort in the live fish fishery of California, and that these
differences must be taken into account in management plans. The lionfish
case poses the opposite scenario, where the manager desires to
erradicate species. To accurately gauge both the effectiveness of
lionfish removal efforts and the resources needed to successfully manage
an invasion, we must acknowledge and understand regional biological
differences in important variables such as allometric growth parameters.

The results presented here have major implications for management. For
example, \citet{edwards_2014} simulated a lionfish culling program under
two scenarios, one using length-at-age and length-to-weight parameters
from North Carolina and one using parameters from Little Cayman. They
showed that using the different parameters caused up to a four-year
difference in the time required for the simulated lionfish population to
recover to 90\% of its initial biomass after removals ceased. Here, we
show that using one set of length-weight parameters versus another for a
given length can result in up to a threefold TW overestimation. These
differences become especially important when allocating resources for
removal programs, incentivizing its fishery as alternative livelihoods,
or estimating ecosystem impacts. Research efforts focused on invasive
lionfish populations need to use parameters calculated for their region
to the extent possible, or at least use reasonable sets of different
parameters that provide upper and lower bounds in their results. This
work additionally highlights the need for more basic research that
furthers our understanding of the invasive lionfish.

>>>>

\author[1]{Juan Carlos Villaseñor-Derbez}
\author[1]{Sean Fitzgerald}
\affil[1]{Bren School of Environmental Sciences and Management, University of California
  Santa Barbara, Santa Barbara, California, USA}
\corrauthor[1]{Juan Carlos Villaseñor-Derbez}{jvillasenor@ucsb.edu}

% \keywords{Keyword1, Keyword2, Keyword3}

\begin{abstract}
Lionfish (\emph{Pterois volitans / miles}) are an invasive species in
the Western Atlantic and the Caribbean. Improving management of invasive
lionfish populations requires accurate estimates of total biomass, which
depend on accurate estimates of the length-weight relationship. Lionfish
exhibit a sedentary behavior that is likely to result in high levels of
spatial variation in some life history characterstics, such as the
length-weight relationship. We review 12 published length-weight
relationships of lionfish taken throughout their invasive range and
describe the spatial variation and implications of these differences.
The spatial pattern observed here is consistent with those reported in
genetic studies or age-at-length studies. We show that the use of
\emph{ex situ} parameters can result in up to a three-fold
overestimation of Total Weight, but that using parameters obtained
nearby reduces this error. These findings can have major implications
for management in terms of predicting effects on local ecosystems,
evaluating the effectiveness of removal programs, or estimating biomass
available for harvest.
\end{abstract}

@@

Lionfish (\emph{Pterois volitans/miles} complex) are an invasive species
in the western Atlantic and Caribbean Sea, likely introduced through
liberation of aquarium-kept organisms \citep{betancurr_2011}. They are
the first invasive marine vertebrates established along the North
Atlantic Caribbean coasts
\citep{schofield_2009,schofield_2010,sabidoitza_2016} and their presence
has been labeled as a major marine invasion because they threaten local
biodiversity, spread rapidly, and are difficult to manage
\citep{hixon_2016}.

Invasive lionfish are primarily studied in coral reef ecosystems, where
their impacts are far-reaching. For example, field experiments by
\citet{albins_2008} showed that lionfish establishment led to reduced
recruitment of native fishes by nearly 80\% over a five week period in
Florida. \citet{green_2012} report that prey fish biomass declined 65\%
over two years as lionfish biomass increased along Bahamian coral reefs.
Lionfish have also established invasive populations in other habitats
such as estuaries, mangroves, hard-bottomed areas, and mesophotic reefs
\citep{jud_2011,barbour_2010,muoz_2011,andradibrown_2017,claydon_2012}.

A substantial amount of research describes lionfish feeding ecology
throughout the invaded range
\citep{muoz_2011,morris_2009,cote_2013,dahl_2014,valdezmoreno_2012,villaseorderbez_2014,hackerott_2017,sandel_2015}.
A meta-analysis by \citet{peake_2018} showed that invasive lionfish prey
on at least 167 different species across the tropical and temperate
North Atlantic. Their feeding behavior and high consumption rates can
reduce recruitment and population sizes of native reef-fish species, and
can further endanger reef fish
\citep{albins_2008, green_2012,rocha_2015}. (However, see
\citet{hackerott_2017} for a case where there was no evidence that
lionfish affected the density, richness, or community composition of
prey fishes). Major efforts have been made to understand the possible
impacts of the invasion by tracking the spread of established lionfish
populations through time \citep{schofield_2009,schofield_2010} and by
predicting invasion ranges under future climates \citep{grieve_2016}.
It\{s been proposed that trophic impacts of lionfish can be minimized if
local lionfish biomass is controled by culling
\citep{ariasgonzalez_2011}.

@@

The feasibility of establishing fisheries through lionfish removal
programs has been extensively evaluated through field observations and
empirical modeling
\citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,chin_2016,usseglio_2017}.
One contributing factor to the success of many removal programs is the
sedentary nature of adult lionfish \citep{jud_2012}. Culling programs
are effective in reducing local adult populations largely because
lionfish exhibit high levels of site fidelity and rarely leave their
home range \citep{Fishelson_1997,cote_2014,kochzius_2005}. Fish with
this sedentary behavior are likely to exhibit high levels of spatial
variation in important life history characterstics such as growth or
natural mortality rates \citep{hutchinson_2008,wilson_2012}. The
importance of considering spatial heterogeneity is well-documented in
terms of assessing and managing sedentary species
\citep{gunderson_2008,guan_2013}, and such variation should be accounted
for when evaluating the feasibility of establishing lionfish fisheries
as well.

Determining the feasibility of such initiatives require modeling changes
in biomass in response to changes in mortality (\emph{i.e.} culling). A
common way to model this is via length-structured population models,
where fish lengths are converted to weight to calculate total biomass
\citep{cote_2014,barbour_2011,andradibrown_2017}. The length-weight
relationship is therefore an essential component of these models, but
this relationship can vary across regions as a response to biotic
(\emph{e.g.} local food availability) and abiotic (\emph{e.g.} water
temperature) conditions \citep{johnson_2016}. Literature suggests that
site-specific parameters are necessary in order to accurately estimate
biomass when length-weight relationships are spatially variable, and
this variability becomes increasingly important when estimating the
potential effectiveness and feasability of lionfish culling programs or
when identifying total biomass available for harvest by fishers
\citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}. In
addition to environmentally-driven spatial variation, genetic analysis
of invasive lionfish suggest biological differences due to the existence
of two genetically distinct subpopulations between the northwest
Atlantic and the Caribbean \citep{betancurr_2011}. To date, no studies
have examined region-wide differences in length-weight parameters
despite the large number of studies reporting this relationship for
lionfish.

@@

We reviewed 12 published studies and obtained 17 length-weight
relationships for the North Atlantic (n = 1), Gulf of Mexico (n = 7),
and Caribbean (n = 10, Table \ref{tab:all_params}, Fig
\ref{fig:all_allo}). We collected information on sampling methods, sex
differentiation, location, and depth ranges from each study when
available, and assumed both genders were included in a study if gender
was unspecified. Only two studies reported parameters for each gender
\citep{aguilarperera_2016,fogg_2013}. Reviewed studies presented
information for organisms obtained at depths between 0.5 m and 57 m.
Three studies explicitly stated that their organisms were sampled with
pole spears
\citep{aguilarperera_2016,chin_2016,dahl_2014,sabidoitz_2016}, and five
studies mentioned that some of their organisms were obtained with pole
spears (or other type of harpoon) but also hand-held nets or fish traps
\citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,sabidoitz_2016,toledohernndez_2014},
and two studies did not specify how organisms were sampled
\citep{deleon_2013,darling_2011}. \citet{fogg_2013} use spine-less
weight in the length-weight relationship estimation, and thus their
parameters likely underestimate total wieght. Since no spine-less to
total weight conversions were available, these parameters were taken as
reported.

@@

Combining the length-weight parameters extracted from the literature and
the additional pair calculated here, we obtain a total of 18 pairs. We
use the central Mexican Caribbean as a case study of how the use of
\emph{ex situ} parameters influences the accuracy of weight estimates
for lionfish. We estimated TW from the TL observations we collected in
the central Mexican Caribbean (n = 109) using each of the 18 parameter
pairs and divided predicted weights by known observed weights to obtain
a simple measure of over- or underestimation. Difference in mean weight
ratios across the different parameter pairs were tested with a one-way
analysis of variance (ANOVA) and Tuskey's test was used for post-hoc
tests. All analyses were performed in R version 3.5.0
\citep{rcore_2018}. Raw data and code used in this work are available at
dryad.org.

@@

The length-weight relationship for organisms from the central Mexican
Caribbean resulted in the coefficient values
\(a = 3.2056297\times 10^{-6}\), \(b = 3.2347391\) and
\(c = -5.4940866\) (\(R^2 = 0.977\), F(df = 1; 107) = 6928.67,
\(p < 0.001\)). The allometric factor (\(b\)) was significantly
different from \(b = 3\) (\(t(107) = 6.04; p<0.001\)) indicating that
lionfish present allometric growth. The length-weight coefficients
estimated in this study were within the range identified by studies in
other regions (Table \ref{tab:all_params}). Figure \ref{fig:l-w-carib}
shows the relationship between TL and TW for this region, and more
information on model fit is presented in Table S2.

Figure \ref{fig:all_allo} shows the length-weight relationships with
parameters from all studies. Parameters from models fit to males or
females exclusively tend to have a higher steepness (\emph{i.e.} higher
allometric parameter), with mean \(\pm\) standard deviation values of
\(b = 3.27 \pm 0.06\) and \(b = 3.31 \pm 0.23\) for males and females
respectively, compared to parameters from models for combined genders
with a mean \(\pm\) standard deviation value of \(b = 3.14 \pm 0.20\).
In the case of the ponderal index (\(a\)) and its \(log_{10}\)
transformation (\(c\)), values were higher for parameters for combined
genders.

There were significant differences in our predicted weights for the
central Mexican Caribbean when using the different pairs of parameters
(\(F(df = 15; 1728) = 38.26; p < 0.001\)). Weight estimates using
parameters from the Gulf of Mexico and North-Western Atlantic were
higher on average than those from the Caribbean. The average (\(\pm\)
SD) predicted-to-observed weight ratios from these three regions were
1.24 \(\pm\) 0.309, 1.76 \(\pm\) 0.496, and 1.17 \(\pm\) 0.398,
respectively. The lowest weight estimates resulted from using the
allometric parameters from Banco Chinchorro in the Caribbean
\citet{sabidoitz_2016}, and the highest weight estimates came from the
Northern Atlantic \citep{barbour_2011}. The calculated ratio of
predicted-to-observed weight ranged from 0.80 \(\pm\) 0.19 to 1.76
\(\pm\) 0.50 (mean \(\pm\) SD). Tukey's post-hoc test suggests that
weight ratios for the central Mexican Caribbean were not differnt from
those obntained with parameters from Little Cayman, the Bahamas, and
some sites in the Gulf of Mexico (Tukeys HSD \(p > 0.05\)).
Predicted-to-observed weight ratios are presented in Figure
\ref{fig:bio_ratio}. Spine-less weight parameters from \citet{fogg_2013}
still produced predicted-to-observed weight ratios \textgreater{} 1.

@@

\caption{\label{tab:unnamed-chunk-5}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study. All parameters have been adjusted to convert from millimeters to grams. n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter for Eq. 1 (presented in $\times 10^{-5}$), c = y-intercept for Eq. 3, b = exponent or slope for Eq. 1 or Eq. 3, respectively. The $R^2$ column indicates reported model fit.}
\centering
\begin{tabular}[t]{llllrrll}
\toprule
Region & Sex & n & a & b & c & \$R\textasciicircum{}2\$ & Reference\\
\midrule
Caribbean & B & 458 & 3.6 & 2.81 & -4.44 & - & Sandel et al., 2015\\
Caribbean & B & 419 & 2.8 & 2.85 & -4.56 & 0.8715 & Chin et al., 2016\\
Caribbean & B & 1450 & 2.3 & 2.89 & -4.64 & 0.96 & de Leon et al., 2013\\
Caribbean & B & 1887 & 0.3 & 3.24 & -5.52 & 0.97 & Edwards et al., 2014\\
Caribbean & B & - & 0.25 & 3.29 & -5.60 & - & Darling et al., 2011\\
\addlinespace
Caribbean & B & 2143 & 0.52 & 3.18 & -5.28 & 0.9907 & Sabido-Itza et al., 2016\\
Caribbean & B & 227 & 0.8 & 3.11 & -5.10 & 0.958 & Toledo-Hernández et al., 2014\\
Caribbean & B & 449 & 0.23 & 3.25 & -5.64 & 0.97 & Sabido-Itza et al., 2016b\\
Caribbean & B & 368 & 0.32 & 3.19 & -5.50 & 0.98 & Sabido-Itza et al., 2016b\\
Caribbean & B & 109 & 0.32 & 3.23 & -5.49 & 0.9766 & This study\\
\addlinespace
GoM & B & 934 & 0.21 & 3.34 & -5.68 & 0.98 & Dahl \& Patterson, 2014\\
GoM & B & 472 & 0.29 & 3.30 & -5.54 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & F & 67 & 0.12 & 3.47 & -5.93 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & M & 59 & 0.42 & 3.23 & -5.38 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & B & 582 & 0.14 & 3.43 & -5.86 & 0.99 & Fogg et al., 2013\\
\addlinespace
GoM & M & 119 & 0.27 & 3.31 & -5.57 & 0.97 & Fogg et al., 2013\\
GoM & F & 115 & 0.68 & 3.14 & -5.17 & 0.94 & Fogg et al., 2013\\
North Atlantic & B & 774 & 2.9 & 2.89 & -4.54 & - & Barbour et al.,2011\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
\caption{\label{fig:all_allo}Length-weight relationships (n = 18) for 12
studies and this study. Colors indicate studies from which the
parameters were extracted. Dotted, dashed and solid lines show models
for males, females, and combined sexes, respectively. The dashed black
line represents the relationship estimated in this study.}
\end{figure}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
\caption{\label{fig:bio_ratio}Violin plot of predicted-to-observed
weight ratios for 18 pairs of allometric parameters. Red and blue
circles indicate median and mean values, respectively. Like letters
indicate values that do not differ significantly.}
\end{figure}

@@

We detected substantial differences in weight-at-length between
organisms from the Caribbean and Gulf of Mexico / North-Western
Atlantic. The groupings of predicted-to-observed weight ratios were
consistent with the spatial distribution of the studies, suggesting that
these differences are mediated by space. These length-weight differences
mirror similar findings of regional variability in age-at-length
relationships of lionfish across both their invaded and native regions
\citep{pusack_2016}. These patterns may be driven by genetic variation
or by organisms being exposed to distinct environmental conditions. For
example, \citet{betancurr_2011} used mitochondrial DNA to demonstrate
the existence of two distinct population groups, identified as the
``Caribbean group'' and ``Northern Group'', and \citet{fogg_2015}
alternatively suggested that age-at-length differences may be driven by
climate. Differences in weight-at-length could also reflect differences
in energy input or differential usage of this energy, or a combination
of both. Future research is needed to determine which processes are at
work here.

Differences in length-weight relationships have traditionally been
highlighted as potential pitfalls to fishery management. For example,
\citet{wilson_2012} show that small-scale variations in length-at-age
and fishing mortality in other Scorpaeniformes translate to differential
landings, effort, and catch per unit effort in the live fish fishery of
California, and that these differences must be taken into account in
management plans. The lionfish case poses the opposite scenario, where
the manager desires to erradicate species. To accurately gauge both the
effectiveness of lionfish removal efforts and the resources needed to
successfully manage an invasion, we must acknowledge and understand
regional biological differences in important variables such as
allometric growth parameters.

The results presented here have major implications for management. For
example, \citet{edwards_2014} simulated a lionfish culling program under
two scenarios, one using length-at-age and length-to-weight parameters
from North Carolina and one using parameters from Little Cayman. Their
results show that using different parameters caused up to a four-year
difference in the time required for the simulated lionfish population to
recover to 90\% of its initial biomass after removals ceased. Here, we
show that using one set of length-weight parameters versus another for a
given length can result in up to a threefold TW overestimation. These
spatially-driven differences become especially important when allocating
resources for lionfish removal programs, incentivizing its fishery as a
source of alternative livelihoods, or estimating ecosystem impacts.
Research efforts focused on invasive lionfish populations need to use
parameters calculated for their region to the extent possible, or at
least use reasonable sets of different parameters that provide upper and
lower bounds in their results.
